---
title: "hw3_jhk2201"
author: "joseph Kim"
date: "10/18/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(p8105.datasets)
data("instacart")
```

### Problem 1 (Description of Instacart Data)

## How many aisles are there, and which aisles are the most items ordered from? 
```{r}

max(instacart$aisle_id)

instacart1 <- instacart %>%
  group_by(aisle) %>% 
  summarise(order_amount=n()) %>% 
  arrange(desc(order_amount)) 
```
There are 134 total aisles listed in the dataframe. The aisle with the most items ordered from was fresh vegetables which had a count of 150609. 

```{r}
instacart2 <- filter(instacart1, order_amount>10000) %>% 
arrange(desc(order_amount)) 

ggplot(instacart2, aes(x = aisle, y = order_amount)) + geom_bar(stat="Identity") +
coord_flip() + labs(title = "Number of Items Ordered for Aisle Greater than 10,000")
              
```

```{r results='asis'}
instacart %>%
      filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
      group_by(aisle, product_name) %>%
      summarize(amount_product = n()) %>%
      arrange(aisle, desc(amount_product)) %>%
      filter(min_rank(desc(amount_product)) <4) %>%
      knitr::kable(digits = 1, caption = "The Top Three Most Popular Items Sold in ")
```

instacart %>%
   mutate(order_dow = recode(order_dow,
                            '0' = 'Sunday',
                            '1' = 'Monday',
                            '2' = "Tuesday",
                            '3' = "Wednesday",
                            '4' = "Thursday",
                            '5' = "Friday",
                            '6' = "Saturday")) %>%
  group_by(product_name, order_dow) %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  summarize(mean_hour_order = mean(order_hour_of_day)) %>%
  pivot_wider(instacart, 
  names_from = order_dow, 
  values_from = product_name)

```

```{r}
data("brfss_smart2010")

behavioral_health = brfss_smart2010 %>%
    janitor::clean_names() %>%
    filter(topic == "Overall Health") %>%
    filter(response %in% c("Excellent", "Very Good", "Good", "Fair", "Poor")) %>%
    mutate(response = as.factor(response)) %>%
    mutate(response = forcats::fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent")))
```

```{r}
data("brfss_smart2010")

behavioral_health2002 = behavioral_health %>%
  filter(year == 2002) %>%
  group_by(locationabbr) %>%
  summarize(count = n_distinct(locationdesc)) %>%
  filter(count >= 7)

behavioral_health2010 = behavioral_health %>%
  filter(year == 2010) %>%
  group_by(locationabbr) %>%
  summarize(count = n_distinct(locationdesc)) %>%
  filter(count >= 7)
```

In 2002, there were six states that were observed at 7 or more locations 
(CT, FL, MA, NC, NJ, PA). In 2021, there were 14 states that fit the above criteria 
(CA, CO, FL, MA, MD, NC, NE, NJ, NY , OH, PA, SC, TX, WA).

```{r}
behave_excellent = behavioral_health %>%
  filter(response == "Excellent") %>%
  group_by(year, locationabbr) %>%
  summarize(avg_datavalue = mean(data_value, na.rm = TRUE)) 

ggplot(behave_excellent, aes(x = year, y = avg_datavalue, color = locationabbr)) + geom_line(aes(group = locationabbr), alpha =0.5) + labs(
    title = "Avergae Data Value Over Time By State",
    x = "Year",
    y = "Average Data Value",
    caption = "Data from brfss"
  )
```



```{r}
plot_data = behavioral_health %>%
  filter(locationabbr == "NY") %>%
  filter(year %in% c("2006", "2008"))
  
ggplot(plot_data, aes(x=response, y=data_value)) + 
  geom_col() + facet_grid(~year) + labs(
    title = "Data_Value Counts for Response Types, By Year",
    x = "Response Types",
    y = "Data Values (%)",
    caption = "Data from brfss") 
```


```{r}
accelerometer_df=
  read_csv("/Users/josephkim/Desktop/p8106_hw3_jhk2201/accel_data.csv") %>%
  janitor::clean_names() %>%
    pivot_longer(
    activity_1:activity_1440,
    names_to = "minute_count", 
    values_to = "activity_count",
    names_prefix = "activity_") %>%
    mutate(
      week = as.integer(week), 
      day_id = as.integer(day_id), 
      minute_count = as.integer(minute_count), 
      weekend_weekday = case_when(
           day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday") ~ "Weekday",
           day %in% c("Saturday", "Sunday") ~ "Weekend")) %>%
      relocate(weekend_weekday,.after = day)
  
```

```{r}

agg.accel_df = accelerometer_df %>%
  group_by(week, day) %>%
  summarize(total_activity = sum(activity_count)) %>%
  knitr::kable(caption = "Total Activity Per Day of the Week")

agg.accel_df
```

```{r}

plot_data3 = accelerometer_df %>%
  group_by(day, minute_count)
  
ggplot(plot_data3, aes(x=minute_count, y=activity_count, color = day)) +
  geom_smooth(se = FALSE) + 
  labs(
   title = "Tracking Activity Over 24 Hours by Day",
    x = "Minutes during the day",
    y = "Total Activity Count") +
  scale_x_continuous(
    breaks = c(0, 120, 240, 360, 480, 600, 720, 840, 960, 1080, 1200, 1320, 1440), 
    labels = c("12 AM", "2 AM", "4 AM", "6 AM", "8 AM", "10 AM", "12 PM", "2 PM", "4 PM", "6 PM", "8 PM", "10 PM", "12 AM"))
```


